Forecasting the 2024 U.S. Presidential Election Results: Linear Regression, Bayesian and Spline-Fit Gaussian Model by Using Pollsters' Data From Five Thirty Eight

### 2024-11-04 paper/paper.qmd
accidentally deleted the repo link

---
title: "Forecasting the 2024 U.S. Presidential Election Results: Linear Regression, Bayesian and Spline-Fit Gaussian Model by Using Pollsters' Data From Five Thirty Eight"
subtitle: "Contrasting Harris's Lead: Strong in Linear Regression and Bayesian Model, Modest in Spline-Fit Gaussian Model"
author: 
  - Ziqi Zhu
  - Yuanchen Miao
  - Claire Chang
thanks: "Code and data are available at: c"
date: today
date-format: long
abstract: "we utilize FiveThirtyEight’s 2024 U.S. presidential poll-of-polls data from [date] to [date] to analyze support trends for the leading candidates, Kamala Harris and Donald Trump. By focusing on variables shows the reliability of a pollster, such as sample size, numeric scores, poll scores, and state-level factors, the data is fit into three models: a linear regression model, a Bayesian model, and a spline-fit Gaussian model. The results of the analysis indicated a strong lead for Harris in both the linear regression and Bayesian models, with a more modest lead in the spline-fit Gaussian model. This paper predicts the potential trajectory of the election, helping the public anticipate the policy directions that might follow a Harris administration."
number-sections: true
bibliography: references.bib
format:
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
---

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election Results: Linear Regression, Bayesian and Spline-Fit Gaussian Model by Using Pollsters' Data From Five Thirty Eight"
subtitle: "Contrasting Harris's Lead: Strong in Linear Regression and Bayesian Model, Modest in Spline-Fit Gaussian Model"
author: 
  - Ziqi Zhu
  - Yuanchen Miao
  - Claire Chang
thanks: "Code and data are available at: https://github.com/zzq20010617/2024_USelection_prediction"
date: today
date-format: long
abstract: "we utilize FiveThirtyEight’s 2024 U.S. presidential poll-of-polls data from [date] to [date] to analyze support trends for the leading candidates, Kamala Harris and Donald Trump. By focusing on variables shows the reliability of a pollster, such as sample size, numeric scores, poll scores, and state-level factors, the data is fit into three models: a linear regression model, a Bayesian model, and a spline-fit Gaussian model. The results of the analysis indicated a strong lead for Harris in both the linear regression and Bayesian models, with a more modest lead in the spline-fit Gaussian model. This paper predicts the potential trajectory of the election, helping the public anticipate the policy directions that might follow a Harris administration."
number-sections: true
bibliography: references.bib
format:
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
---
